On the Bit Complexity of Finding Points in Connected Components of a Smooth Real Hypersurface

### 2020-02-07 main.tex
Update main.tex
Bernoulli's inequality

  As part of the randomization, the algorithm chooses a set 
  \[
  S := \{1,2,\hdots,\epsilon^{-2}3n^2(2d)^{2n}\}
  \]
  from which to sample from.

  With probability at least $1-\epsilon$, the output is correct. Otherwise, either a proper subset of the points is produced, or FAIL.  In any case, the algorithm uses
  \[
  O^{\sim}(nk(Lb+d^{2n}(s + \log 1/\epsilon^2+d)(L+d)\log(s + \log 1/\epsilon^2)))
  \]
  bit operations, with $k \geq -\lg(1-(1+\epsilon)^{(-1/n)})$. The polynomials in
  the output have degree at most $d^n,$ and height 
  \[
  O^{\sim}((s+\lg 1/\epsilon^2 + d)d^n)
  =O^{\sim}((s+\lg 1/\epsilon^2)d^{n+1}).
  \]
\end{theorem}

The runtime for cases without a strait-line program in the input are as follows. In these cases a polynomial $f$ of degree $d$ is given in the input, and a strait-line program is built for it by computing all the terms. In this case, $L \geq d^n$ and $b \geq \htt(f) = s,$ so that the number of bit operations becomes
\begin{align*}
&O^{\sim}(nk(d^ns+d^{2n}(s + \log 1/\epsilon^2+d)(d^n+d)\log(s + \log 1/\epsilon^2)))\\
      &= 
O^{\sim}(nk(d^ns+(d^{3n}+d^{2n+1})(s + \log 1/\epsilon^2+d)\log(s + \log 1/\epsilon^2)))\\
     &= 
O^{\sim}(nk(d^{3n}(s + \log 1/\epsilon^2+d)\log(s + \log 1/\epsilon^2)))\\
     &= 
O^{\sim}(nk(d^{3n+1}(s + \log 1/\epsilon^2)\log(s + \log 1/\epsilon^2))),
\end{align*}
and the degree and height of the output does not change.

@@

  As part of the randomization, the algorithm chooses a set 
  \[
  S := \{1,2,\hdots,\epsilon^{-2}3n^2(2d)^{3n}\}
  \]
  from which to sample from.

@@

  O^{\sim}(nk(Lb+d^{2n}(s + \log 1/\epsilon^2+d)(L+d)\log(s + \log 1/\epsilon^2)))

@@

  bit operations, with $k \geq -\lg(1-(1+\epsilon)^{(-1/n)})$. The polynomials in

@@

  O^{\sim}((s+\lg 1/\epsilon^2 + d)d^n)
  =O^{\sim}((s+\lg 1/\epsilon^2)d^{n+1}).

@@

\nl Take  $S := \{1,2,\hdots,\epsilon^{-2}3n^2(2d)^{3n}\}$

@@

\nl Run \cite[Algorithm 2]{SH} $k \geq -\lg(1-(1+\epsilon)^{(-1/n)})$ times with input (state this in terms of straight line programs?)

@@

    \item We defined $S = \{1,2,\hdots,\epsilon^{-2}3n^2(2d)^{3n}\}$ and therefore the height of $a_{i,j} \in S$ is at most 

@@

    \log 1/{\epsilon^2} + \log(3n^2(2d)^{2n}) = O^{\sim}(\log 1/{\epsilon^2}).

@@

        O^{\sim}(n\log n + \log 1/{\epsilon^2})\\
        &= O^{\sim}(\log 1/{\epsilon^2}).

@@

Let $\mathscr{E}$ be the event that, the parameterizations $[\mathscr{Q}_1,\hdots,\mathscr{Q}_n]$ returned in step 7 of Algorithm 1 contain all points and are correct. Then, 
\begin{align*}
\pr[\textrm{success}] = \pr[A \not\in \Delta] \times \pr[\mathscr{E}~|~A \not\in \Delta].  
\end{align*}
By construction of $S$,
\[
\pr[A \not\in \Delta] = 1-\pr[A \in \Delta] \geq
1-\epsilon^2.
\]
Thus, 
\begin{align*}
\pr[\textrm{success}] &\geq  (1-\epsilon^2)\pr[\mathscr{E}~|~A \not\in \Delta]\\
&\geq (1-\epsilon^2)(1-(11/32)^k)^n\\
& \geq (1-\epsilon^2)(1-2^{-k})^n= 1-\epsilon
\end{align*}
if and only if 
\[
(1+\epsilon)(1-2^{-k})^n= 1,
\]
if and only if 
\[
k \geq -\lg\left ( 1 - (1+\epsilon)^{(-1/n)} \right ).
\]
%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-base}
%%
\end{document}
\endinput
%%

>>>>

  As part of the randomization, the algorithm chooses a set 
  \[
  S := \{1,2,\hdots,2\epsilon^{-1}3n^2(2d)^{2n}\}
  \]
  from which to sample from.

  With probability at least $1-\epsilon$, the output is correct. Otherwise, either a proper subset of the points is produced, or FAIL.  In any case, the algorithm uses
  \[
  O^{\sim}(nk(Lb+d^{2n}(s + \log 1/\epsilon+d)(L+d)\log(s + \log 1/\epsilon)))
  \]
  bit operations, with $k \geq 1 + \lg n + \lg(1/\epsilon)$. The polynomials in
  the output have degree at most $d^n,$ and height 
  \[
  O^{\sim}((s+\lg 1/\epsilon + d)d^n)
  =O^{\sim}((s+\lg 1/\epsilon)d^{n+1}).
  \]
\end{theorem}

The runtime for cases without a strait-line program in the input are as follows. In these cases a polynomial $f$ of degree $d$ is given in the input, and a strait-line program is built for it by computing all the terms. In this case, $L \geq d^n$ and $b \geq \htt(f) = s,$ so that the number of bit operations becomes
\begin{align*}
&O^{\sim}(nk(d^ns+d^{2n}(s + \log 1/\epsilon+d)(d^n+d)\log(s + \log 1/\epsilon)))\\
      &= 
O^{\sim}(nk(d^ns+(d^{3n}+d^{2n+1})(s + \log 1/\epsilon+d)\log(s + \log 1/\epsilon)))\\
     &= 
O^{\sim}(nk(d^{3n}(s + \log 1/\epsilon+d)\log(s + \log 1/\epsilon)))\\
     &= 
O^{\sim}(nk(d^{3n+1}(s + \log 1/\epsilon)\log(s + \log 1/\epsilon))),
\end{align*}
and the degree and height of the output does not change.

@@

  As part of the randomization, the algorithm chooses a set 
  \[
  S := \{1,2,\hdots,2\epsilon^{-1}3n^2(2d)^{3n}\}
  \]
  from which to sample from.

@@

  O^{\sim}(nk(Lb+d^{2n}(s + \log 1/\epsilon+d)(L+d)\log(s + \log 1/\epsilon)))

@@

  bit operations, with $k \geq 1+\lg n + \lg(1/\epsilon)$. The polynomials in

@@

  O^{\sim}((s+\lg 1/\epsilon + d)d^n)
  =O^{\sim}((s+\lg 1/\epsilon)d^{n+1}).

@@

\nl Take  $S := \{1,2,\hdots,2\epsilon^{-1}3n^2(2d)^{3n}\}$

@@

\nl Run \cite[Algorithm 2]{SH} $k \geq 1+\lg n + \lg(1/\epsilon)$ times with input (state this in terms of straight line programs?)

@@

    \item We defined $S = \{1,2,\hdots,2\epsilon^{-1}3n^2(2d)^{3n}\}$ and therefore the height of $a_{i,j} \in S$ is at most 

@@

    \log 1/{\epsilon} + \log(3n^2(2d)^{2n}) = O^{\sim}(\log 1/{\epsilon}).

@@

        O^{\sim}(n\log n + \log 1/{\epsilon})\\
        &= O^{\sim}(\log 1/{\epsilon}).

@@

Let $\mathscr{E}$ be the event that, the parameterizations $[\mathscr{Q}_1,\hdots,\mathscr{Q}_n]$ returned in step 7 of Algorithm 1 contain all points and are correct. Then, 
\begin{align*}
\pr[\textrm{success}] = \pr[A \not\in \Delta] \times \pr[\mathscr{E}~|~A \not\in \Delta].  
\end{align*}
By construction of $S$,
\[
\pr[A \not\in \Delta] = 1-\pr[A \in \Delta] \geq
1-\epsilon/2.
\]
Now set $k = \lg(2n/\epsilon)$ so that 
\[
(1-2^{-k})^n = (1 - \epsilon/(2n))^n \geq 1 - \epsilon/2,
\]
by Bernoulli's inequality. Therefore, 
\begin{align*}
\pr[\textrm{success}] &\geq  (1-\epsilon/2)\pr[\mathscr{E}~|~A \not\in \Delta]\\
&\geq (1-\epsilon/2)(1-(11/32)^k)^n\\
& \geq (1-\epsilon/2)(1-2^{-k})^n \\
& \geq (1-\epsilon/2)(1-\epsilon/2)\\
& = 1 - \epsilon + \epsilon^2/4 \geq 1- \epsilon.
\end{align*}
%%
%% The next two lines define the bibliography style to be used, and
%% the bibliography file.
\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-base}
%%
\end{document}
\endinput
